Modalities for Location Virtualization

### 2022-09-19 intro.tex

We develop these ideas in an Iris-based\mytodo{cite JFP} separation logic, and verify simplified versions of several critical virtual-memory-related pieces of OS functionality, including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory.\mytodo{colin finish}

>>>>

We develop these ideas in an Iris-based\mytodo{cite JFP} separation logic, and verify simplified versions of several critical virtual-memory-related pieces of OS functionality, including mapping and unmapping pages, and describing the self-referential identity maps used in most kernels to allow convenient access to physical memory.
